---
title: "Aplication Pitch Presentation"
author: "Janick Reales"
date: "03/August/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## App description  

This aplication can be used to study the relationship between the speed and the distance reached by a car. The data used was taken from the CARS data set. You can fit the regression lines, show the leats squared lines and see a prediction made by the model for a given speed value and its dist value over the red line.
The application also shows the diagnostics plots, where the user can select a number from 1 to 6 and see the respective diagnostic plot he/she wants to explore.  


## Model summary  
The characteristics of the fitted model are the following.  

```{r comment=""}
## Fitting the model 
modelFit <- lm(dist~speed, data=cars)

### summary
summary(modelFit)
```  

## CARS data set plot  

After fitting the model, I plotted it with the data.  

```{r}
##plot
plot(cars$speed, cars$dist, xlab="Speed", ylab="Distance",
     main="Car speed vs distance", pch=19, col="grey", lwd=2)
abline(modelFit, lwd=2, col="red")
```   

## Diagnostics plots  

```{r}
## diagnostics
par(mfrow=c(2,2))

for (i in 1:4){
    plot(modelFit,i)
}
```  




